% !TeX encoding = UTF-8
% !TeX spellcheck = en_GB

%%% Add [final] option to the report class to switch between draft and final version of the report
%%% Use [narrowmargin] to enable narrow margins - this may impair readability.
%\documentclass[a4paper,12pt,draft]{include/intocpsreport}   %Or
\documentclass[a4paper,12pt,final]{include/intocpsassociation}   %Or
% intocpslargereport if chapters are required.
%
%
%
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{tikz-uml}
\usepackage{framed}
\usepackage{subcaption}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{color}
\usepackage{amsmath}
\usepackage{courier}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{textcomp} % Used for 20-sim section \textrightarrow
%\usepackage{showframe}

\usepackage{listings}
\usepackage{glossaries}

%% Define listing environment for XML
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
  basicstyle=\footnotesize\ttfamily,
  columns=fullflexible,
  showstringspaces=false,
  commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{XML}
{
  morestring=[b]",
  morestring=[s]{>}{<},
  morecomment=[s]{<?}{?>},
  stringstyle=\color{black},
  identifierstyle=\color{darkblue},
  keywordstyle=\color{cyan},
  morekeywords={xmlns,version,type}% list your attributes here
}


\lstnewenvironment{xml}[1][]{\lstset{  language=XML,
  morekeywords={encoding, xs:schema,xs:element,xs:complexType,xs:sequence,xs:attribute}}\lstset{#1}}
{}

%% end listing environment for XML
%
%
%
\def\draftnote#1{\noindent\smallskip\framebox{\begin{minipage}{0.95\columnwidth}\color{red}#1\end{minipage}}\smallskip\par}
\newenvironment{draftnoteenv}{\noindent\smallskip\begin{framed}\begin{minipage}{0.95\columnwidth}\color{red}}{\end{minipage}\end{framed}\smallskip\par}
\newenvironment{assumption}{\noindent\smallskip\color{blue}\begin{framed}\begin{minipage}{0.95\columnwidth}}{\end{minipage}\end{framed}\smallskip\par}
%
%
%
\newcommand{\revisit}[1]{\textcolor{red}{\pmb{[[[}\@ #1\@ \pmb{]]]}}}
%
%
\reporttitle{INTO-CPS Maestro Documentation}
\shortreporttitle{INTO-CPS Maestro Documentation}  %To use if report title is too long for header
%
%
%
%%% Set document release class as appropriate
%%% e.g. Public, Restricted, Programme Participant
\reportstatus{Public Draft}
%
%
%
%%% If document is a deliverable, this flag should be commented out
%%% e.g. %\technotetrue
%%% If report is a technical report, leave uncommented
%%% e.g. \technotetrue
\technotetrue % Comment out as appropriate
%
%
%
\submissiondate{}
\contributors{
Casper Thule, Aarhus University, Centre for Digital Twins \\
Kenneth Lausdahl, Mj{\o}lner Informatics A/S \\
Cl\'audio Gomes, Aarhus University, Centre for Digital Twins \\
Hugo Daniel Macedo, Aarhus University, Centre for Digital Twins

}
%
%
%
\editors{
Casper Thule, Aarhus University, Centre for Digital Twins \\
}
%
%
%
%\reviewers{Ken Pierce, UNEW\\
%Kangfeng Ye, UY\\
%Luis Diogo Couto, UTRC}
%
%
%
%% Version details
% #1: version
% #2: date
% #3: author
% #4: description
\addversion{0.01}{November 18, 2019}{Casper Thule}{Initial Version.}

%
%
\begin{document}
\maketitle
%
%
%
%%%% Document abstract page %%%%
\section*{Abstract}
\label{sec:abstract}
%
Maestro is a co-simulation orchestration engine for FMI 2.0 originally developed as part of the INTO-CPS project from 2016-2018. This publication
concerns the new Maestro that will take over for the existing tool.

The motivation for recreating Maestro is to make it more flexible and provide
better support for verification. This will be carried out by defining a language
called Maestro Base Language (MaBL) that can be used to create a specification
of a co-simulation to be carried out. The flexibility is introduced by enabling
the possibility to combine the constructs of the language in various ways to
support different scenarios. Having a specification of a co-simulation that can
be passed to verification tools is an improvement in terms of verification, as
it is now clear what is to be executed. MaBL has been constrained in in order to
simplify this process. Finally, Maestro will also incorporate a runtime that can
execute MaBL specifications.

The flexibility is also expressed in the nature of creating a specification and
verifying it, as these phases are based on plugins. Furthermore, plugins can be composed such
that they jointly represent a specification or multiple verification efforts. Thus, if something is
missing in order to support a certain scenario or verification task, it is
possible to create a plugin that Maestro will make use of.


The ambition is that Maestro can support both research-oriented efforts in
co-simulation but also industry-related activities. As the development is in
progress, the Maestro team is very interested in feedback, features, use cases,
plugins and similar. The repository is available at \url{https://github.com/into-cps-association/maestrov2}
\newpage
%
%%%% Document table of contents page %%%%
\tableofcontents
\newpage
%
%
%
%%%% Document Content %%%%
%% \chapter{Chapter Title} %% if intocpslargereport is in use
%\begin{assumption}
%
%
%
\input{sections/intro.tex}
\clearpage
\input{sections/features_use-cases.tex}
\clearpage
\input{sections/approach.tex}
\clearpage
\input{sections/mabl.tex}
\clearpage
\input{sections/plugins.tex}
\clearpage
\input{sections/examples.tex}
\clearpage
\input{sections/future_work.tex}
\clearpage
\input{sections/legacy_context.tex}
\clearpage
\input{sections/legacy_intro.tex}
\clearpage
%
%
%
%
%%%% Bibliography %%%%
\bibliographystyle{alpha}
\bibliography{bibliography}
\label{ch:bib} %label to refer to
%
%
%
\clearpage
%
%
%
\appendix
\input{appendices/acronyms.tex}
\clearpage
%
%
%
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
