\section{Context}
The Context contains information available to Maestro-Program,
plugins and Maestro-Runtime. These entities can also add information to the
Context by creating a new Context.

\subsection{Context Structure}
This section describes the structure of the Root Context and thereby what is
supported natively. The reason for natively supporting some data is that it is
considered essential for FMI co-simulation.
First, the entries are presented with an overall description. Afterwards, the types
mentioned in the overall description are described. Note, that not all entries are populated
by Maestro-Program prior to employing plugins. Some of these entries will be
populated by plugins. TODO: Clearly describe which entries Maestro-Program
populates.
\paragraph{Overall Structure}
\begin{description}
  \item[RawFMUs] The raw FMU information. Perhaps from a UI. Type: Map[FmuKey, FmuPath]
  \item[RawInstances] The raw instance information. Perhaps from a UI. Type: Map[FmuKey, List[InstanceKey]]
  \item[RawConnections] The raw connections information. Perhaps from a UI.
    Type: Map[{FmuKey, FmuInstance, ScalarVariableName}, Set[{FmuKey, FmuInstance, ScalarVariableName}]]
  \item[RawParameters] The raw parameters information. Perhaps from a UI.
    Type: Map[ParameterKey, Value] and Map[FMU, Map[Instance,
    Map[ScalarVariableName, ParameterKey]]]
  \item[Parameters] Parsed parameter information. Map[ScalarVariableID]
  \item[FMUsWithInstances] Enriches RawFMUs with ModelDescription information
    and connects FMUs to their respective instances. Type: Map[Fmu, Set[Instance]]
  \item[Connections] The connections based on FMUsWithInstances and variables
    from the corresponding ModelDescription files. Type: Set[Connection]
  \item[SortedDependantVariables] An list that describes the order of setting
    and getting dependant scalar variables according to internal and external
    dependencies. Type: List[ScalarVariableID]
    \item[Custom] This entry can be used freely. Type: Map[CustomDataKey, Any].
\end{description}

\paragraph{Types}
\begin{description}
  \item[FmuKey] String: Unique identifier for a given FMU
  \item[FmuPath] URI: Location of the FMU
  \item[InstanceKey] String: Unique identifier for a given instance
  \item[ScalarVariableName] String: Name of a given scalar variable.
    TODO: Perhaps valuereference, perhaps both?
  \item[Fmu] Data Object with FmuKey, FmuPath, ModelDescription.
  \item[Instance] Data Object that consists of parent FMU and InstanceKey
  \item[ModelDescription] The parsed model description.
  \item[Connection] Data Object with from of type ScalarVariableID and to of type Set[ScalarVariableID]
  \item[ScalarVariableID] Data Object that consists of Instance and ScalarVariableValueReference
  \item[CustomDataKey] String: Unique identifier for some custom data.
  \item[Any] Represents the value associated with a CustomDataKey.
    TODO: Represent as Sum Type: Any (Any) | JSON (String) | Text (String) |
    Byte (Array[Byte]) | ?
\end{description}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Maestro"
%%% End:
